Use of management strategy evaluation to inform fisheries management in a changing climate

### 2019-09-03 Poster_ICES.Rmd
Edits based on feedback; header spelling; figure captions; sdm citation;

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0
#ESSENTIALS
title: Use of management strategy evaluation to inform fisheries management in a changing climate
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings: "Explicit documentation of MSE processes is limited. <br> <br> Climate change MSEs have been less explict, more scientist driven, included fewer objectives -- with less consideration of economic or social objectives -- and fewer drivers."
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: MSEreview.bib
link-citations: true
nocite: '@*'
title_textsize: "50pt"
main_textsize: "90pt"
column_numbers: 3
body_textsize: "29.5pt"
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

@@

Adaptive management arose to address uncertainties and accelerate progress towards meeting management objectives. Using the structured decision making (SDM) process -- the decision making framework in which adaptive management occurs -- as our framework, how do published MSE projects utilize standard SDM components and support learning within the MSE practitioner community?

@@

```{r explicit, fig.cap='Percentage of MSEs that included explicit documentation of these SDM process steps!', fig.height=6, out.width="100%"}
text1<-expression(paste("Absent or \nInexplicit"))
text2<-paste("Absent")
text3<-paste("Unknown")
Freq.plot + annotate("text", x = 5, y = 55, label = text1, size=25) + 
  annotate("text", x = 2.6, y = 50, label = text2, size=20) + 
  annotate("text", x = 1, y = 50, label = text3, size=12)
```

@@

```{r participants, fig.cap='Who participated during these stages of the SDM process', fig.height=6, out.width="100%"}
Part.plot
```

@@

```{r driversPlot, fig.cap='text', fig.height=6, out.width="100%"}
Driver.plot
```

>>>>

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0
#ESSENTIALS
title: Use of management strategy evaluation to inform fisheries management in a changing climate
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings: "Explicit documentation of management strategy evaluation processes is limited. <br> <br> Climate change MSEs have been less explicit, more scientist driven, included fewer objectives -- with less consideration of economic or social objectives -- and fewer drivers."
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: MSEreview.bib
link-citations: true
nocite: '@*'
title_textsize: "50pt"
main_textsize: "90pt"
column_numbers: 3
body_textsize: "29.5pt"
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

@@

Adaptive management arose to address uncertainties and accelerate progress towards meeting management objectives. Using the structured decision making (SDM) process [@R-SDM] -- the decision making framework in which adaptive management occurs -- as our framework, how do published MSE projects utilize standard SDM components and support learning within the MSE practitioner community?

@@

```{r explicit, fig.cap='Percentage of MSEs that included explicit documentation (colored bars) of SDM process steps --- Roles and meetings --- and adoption of results. In the remaining MSEs was documentation was inexplicit, or absent, and whether the results were adopted was unknown.', fig.height=6, out.width="100%"}
text1<-expression(paste("Inexplicit \nor Absent"))
text2<-paste("Absent")
text3<-paste("Unknown")
Freq.plot + annotate("text", x = 5, y = 55, label = text1, size=25) + 
  annotate("text", x = 2.6, y = 50, label = text2, size=20) + 
  annotate("text", x = 1, y = 50, label = text3, size=12)
```

@@

```{r participants, fig.cap='Who guided, participated in, or provided input during the specified steps of the MSE process', fig.height=6, out.width="100%"}
Part.plot
```

@@

```{r driversPlot, fig.cap='Drivers included in MSE models', fig.height=6, out.width="100%"}
Driver.plot
```
